### 2024-06-24 basic-statistics.qmd
20240624 - power

```{r}
pwr::pwr.t.test(
  n = N,
  d = effectSize_d,
  sig.level = alpha,
  type = "two.sample",
  alternative = "two.sided")
```

@@

```{r}
pwr::pwr.t.test(
  d = effectSize_d,
  power = power,
  sig.level = alpha,
  type = "two.sample",
  alternative = "two.sided")
```

@@

```{r}
pwr::pwr.t.test(
  n = N,
  power = power,
  sig.level = alpha,
  type = "two.sample",
  alternative = "two.sided")
```

>>>>

```{r}
pwr::pwr.t.test( # balanced group sizes
  n = N,
  d = effectSize_d,
  sig.level = alpha,
  type = "two.sample",
  alternative = "two.sided")

pwr::pwr.t2n.test( # unbalanced group sizes
  n1 = nGroup1,
  n2 = nGroup2,
  d = effectSize_d,
  sig.level = alpha,
  alternative = "two.sided")
```

@@

```{r}
pwr::pwr.t.test( # balanced group sizes
  d = effectSize_d,
  power = power,
  sig.level = alpha,
  type = "two.sample",
  alternative = "two.sided")

pwr::pwr.t2n.test( # unbalanced group sizes
  n1 = nGroup1,
  d = effectSize_d,
  power = power,
  sig.level = alpha,
  alternative = "two.sided")
```

@@

```{r}
pwr::pwr.t.test( # balanced group sizes
  n = N,
  power = power,
  sig.level = alpha,
  type = "two.sample",
  alternative = "two.sided")

pwr::pwr.t2n.test( # unbalanced group sizes
  n1 = nGroup1,
  n2 = nGroup2,
  power = power,
  sig.level = alpha,
  alternative = "two.sided")
```
